### 2016-05-14 paper.tex
from phils initial email

\documentclass{article}

\usepackage[letterpaper, margin=1.0in]{geometry}

\begin{document}

\title{Attestable Expiration with Trusted Platform Modules}
\author{Frank Cangialosi, Philip Kim}

\maketitle

\section{Introduction}

Why it would be desirable to have information expire...

The difficult problem in implementing information that expires is the impossibility of proving a negative. Even if it were possible for the recipient to prove that he has deleted the sensitive information, he can not prove that he didn't make a copy of it beforehand.

This changes with the use of TPMs. With TPMs, it is possible to seal information such that it can only be accessed by a trusted program. Moreover, one can provably attest that the trusted program was executed with a given input and produced a given output.

Background on TPMs...

sealed storage
Secure channel
Protection against replay attacks

\section{Related Work}

Vanish\\

Flicker\\

Ethereum\\

\section{Design}

Suppose that Alice wishes to send a message to Bob that expires at time $t$. In our model, Bob is not malicious and will not attempt to store an illicit copy of the message. However, we wish to protect against the eventuality that Bob becomes malicious in the future, or that Bob's credentials are compromised by a future adversary (Mallory).

We wish to achieve the following properties:

\begin{itemize}

\item Before time $t$, Bob can read the message.
\item After time $t$, Bob can not read the message.
\item Alice does not need to be online after sending the message for Bob to be able to read it.

\end{itemize}

Strawman 1:
  Alice sends the message to Bob, encrypted with a key K. She stores K on a trusted third party Charlie. To read the data, Bob asks Charlie for the key, and if the current time is < T, Charlie gives it to him. Alice trusts Bob not to save a copy of the key.

  The strawman fails because there is nothing stopping Charlie from retaining K even after T. Therefore, Mallory can collude with Charlie to obtain K and read the message.

Proposal:
  In this model, Charlie is a provider of secure computing; he wants to a) collect fees, and b) preserve his reputation. Assume that Charlie is running Flicker.

\begin{enumerate}

\item Alice sends a Flicker PAL (Piece of Application Logic) to Charlie. Alice asks Charlie to run it with the input parameter "-bootstrap".

\item When Charlie runs the PAL, the PAL establishes a secure channel as per section 4.4.2 of the Flicker paper. That is, it generates a public/private key pair, outputs the public key, and puts the private key in sealed storage.

\item Charlie sends Alice a Flicker attestation of the execution and output. After verifying the attestation, Alice knows that a) her PAL was executed, and b) it produced the attested public key.

\item Alice encrypts K with the secure channel public key sends it to Charlie. Charlie stores the ciphertext of the key. Alice then goes offline, but not before completing step 7 below.

\item In order to request K, Bob sends his public key to Charlie. Charlie runs the PAL with three inputs: the "-divulge" flag, the ciphertext of K, and Bob's public key. The PAL decrypts K using the secure channel private key, re-encrypts it using Bob's public key, and produces the re-encrypted key as output. Charlie sends the output to Bob.

\item If Charlie runs the PAL with the parameter "-destroy", the PAL will sign the statement "Key destroyed" with the secure channel private key. It will then destroy the secure channel private key. The output is the signed statement.

\item Before going offline, Alice wrote an Ethereum contract that said, "If Charlie provides a statement that reads 'Key destroyed' when decrypted with this secure channel public key, I will pay him X ether."

\end{enumerate}

\section{Analysis}

Properties achieved:

\begin{enumerate}

\item Charlie never learns K.

\item If Charlie produces proof that he destroyed the key, then a) he gets rewarded, and b) Alice knows that K can never be divulged again. (Note: in order to know that the secure channel private key was truly destroyed, we have to protect against replay attacks using a secure counter as in Flicker section 4.3.2.)

\item If Charlie doesn't claim his key-destruction payment before time T, Alice knows that something is wrong. We can strengthen this to "Charlie loses reputation" by having him sign a promise to destroy the key at the start.

\end{enumerate}

\end{document}

### 2016-05-17 paper.tex
Few "Design" paragraphs.

@@
 Suppose that Alice wishes to send a message to Bob that expires at time $t$.
-In our model, Bob is not malicious and will not attempt to store an illicit copy of the message.
-However, we wish to protect against the eventuality that Bob becomes malicious in the future, or that Bob's credentials are compromised by a future adversary (Mallory).
+That is, before time $t$ Bob is able to read the message, but after time $t$ Bob is unable to read the message.
+In our model, Bob is not malicious and will not attempt to make an illicit copy of the message.
+However, we wish to protect against the eventuality that Bob becomes malicious in the future, or that Bob's system is compromised by a future adversary (Mallory).
+We do not wish to require that Alice be online in order for Bob to receive or read the message.
 
-We wish to achieve the following properties:
+As a straw man, Alice could send the message to Bob encrypted with key $K$, and then store $K$ on a trusted third party (Charlie).
+To read the data, Bob asks Charlie for $K$, and if the current time is less than $t$, Charlie gives it to him.
+Just as we assume that Bob will not make a copy of the message, we assume that he discards $K$ after each use.
 
-\begin{itemize}
+The problem with the straw man is that it requires extending the same trust to Charlie that we do to Bob.
+Charlie can retain $K$ as long as he likes and distribute it as widely as he wishes---e.g., to Mallory---and moreover he can repudiate doing so without any way for Alice to prove otherwise.
 
-\item Before time $t$, Bob can read the message.
-\item After time $t$, Bob can not read the message.
-\item Alice does not need to be online after sending the message for Bob to be able to read it.
-
-\end{itemize}
-
-Strawman 1:
-  Alice sends the message to Bob, encrypted with a key K.
-She stores K on a trusted third party Charlie.
-To read the data, Bob asks Charlie for the key, and if the current time is < T, Charlie gives it to him.
-Alice trusts Bob not to save a copy of the key.
-
-  The strawman fails because there is nothing stopping Charlie from retaining K even after T. Therefore, Mallory can collude with Charlie to obtain K and read the message.
-
-Proposal:
-  In this model, Charlie is a provider of secure computing; he wants to a) collect fees, and b) preserve his reputation. Assume that Charlie is running Flicker.
+Through use of a TPM, we can shift the burden of proof onto Charlie; instead of Alice proving that Charlie acted in bad faith, Charlie can prove that he acted correctly.
+Suppose, for example, that we extend the model such that Charlie is a provider of secure computing.
+In exchange for a fee, he will provide attestable execution of a given program at a given time.
 

### 2016-05-17 paper.tex
More on the protocol

@@
 The problem with the straw man is that it requires extending the same trust to Charlie that we do to Bob.
-Charlie can retain $K$ as long as he likes and distribute it as widely as he wishes---e.g., to Mallory---and moreover he can repudiate doing so without any way for Alice to prove otherwise.
+Charlie can retain $K$ as long as he likes and distribute it as widely as he wishes---e.g., to Mallory---and moreover he can repudiate his misbehavior without any way for Alice to prove otherwise.
 
@@
 
+Alice and Charlie can perform a protocol as follows:
+
 \begin{enumerate}
 
-\item Alice sends a Flicker PAL (Piece of Application Logic) to Charlie. Alice asks Charlie to run it with the input parameter "-bootstrap".
+\item Alice sends a Flicker PAL to Charlie. The PAL has an input parameter called `mode' which can take one of the following values: `initialize', `divulge', or `destroy'.
 
-\item When Charlie runs the PAL, the PAL establishes a secure channel as per section 4.4.2 of the Flicker paper.
-That is, it generates a public/private key pair, outputs the public key, and puts the private key in sealed storage.
+\item Alice asks Charlie to run the PAL with the input `mode=initialize'.
+When Charlie runs the PAL, the PAL establishes a secure channel.
+That is, it generates a public/private key pair, outputs the public key, and stores the private key in the TPM such that only this PAL is able to read it.
 
-\item Charlie sends Alice a Flicker attestation of the execution and output. After verifying the attestation, Alice knows that a) her PAL was executed, and b) it produced the attested public key.
+\item Charlie sends Alice the PAL's output as well as a Flicker attestation of the execution.
+After verifying the attestation, Alice knows that a) her PAL was executed, and b) it produced the attested public key.
 
-\item Alice encrypts K with the secure channel public key sends it to Charlie. Charlie stores the ciphertext of the key. Alice then goes offline, but not before completing step 7 below.
+\item Alice encrypts $K$ with the secure channel public key and sends it to Charlie.
+Charlie stores the ciphertext of $K$.
+Alice then goes offline, but not before writing an Ethereum contract, described below as step 8.
 
-\item In order to request K, Bob sends his public key to Charlie.
-Charlie runs the PAL with three inputs: the "-divulge" flag, the ciphertext of K, and Bob's public key.
-The PAL decrypts K using the secure channel private key, re-encrypts it using Bob's public key, and produces the re-encrypted key as output.
+\item In order to request $K$, Bob sends his public key to Charlie.
+Charlie runs the PAL with three inputs: `mode=divulge', the ciphertext of $K$, and Bob's public key.
+The PAL decrypts $K$ using the secure channel private key, re-encrypts it using Bob's public key, and produces the re-encrypted key as output.
 Charlie sends the output to Bob.
 
-\item If Charlie runs the PAL with the parameter "-destroy", the PAL will sign the statement "Key destroyed" with the secure channel private key.
+\item When the PAL is run using `mode=divulge', it also produces as output an append-only log that contains one entry for every public key to whom Charlie has divulged $K$.
+The log is signed using the secure channel private key.
+This log must be included on subsequent executions that use `mode=divulge' so that the PAL can add another entry if necessary.
+The PAL can confirm that the required log has been provided and protect against replay attacks by using a monotonic counter, described in Flicker 4.3.2.
+
+\item If Charlie runs the PAL with inputs comprising `mode=destroy' and the divulgence log, the PAL will append to the log the statement ``key destroyed''.
 It will then destroy the secure channel private key.
-The output is the signed statement.
 
-\item Before going offline, Alice wrote an Ethereum contract that said, "If Charlie provides a statement that reads 'Key destroyed' when decrypted with this secure channel public key, I will pay him X ether."
+\item Before going offline, Alice wrote an Ethereum contract that said, ``If Charlie publishes before time $t$ a log that can be decrypted using this public key and whose last entry is ``key destroyed", I will pay him $X$ ether."
 
@@
 \section{Analysis}
+
+If Charlie produces proof that he destroyed the key, he earns his commission and Alice knows that $K$ can never be divulged again.
+If he never claims his commission, then Alice knows that something is wrong.
+Although she can not prove
 
@@
 
+Note that the protocol as written does not restrict to whom Charlie divulges the key. However, it produces a non-repudiable record of the persons to whom it has been divulged.
+
 \end{enumerate}

### 2016-05-17 paper.tex
Analysis.

@@
 If Charlie produces proof that he destroyed the key, he earns his commission and Alice knows that $K$ can never be divulged again.
-If he never claims his commission, then Alice knows that something is wrong.
-Although she can not prove
+If he does not claim his commission before time $t$, then Alice knows that something is wrong.
+We can tie the protocol into a reputation system by requiring as step 0 that Charlie make a public, signed commitment to fulfilling the contract.
 
-Properties achieved:
-
-\begin{enumerate}
-
-\item Charlie never learns K.
-
-\item If Charlie produces proof that he destroyed the key, then a) he gets rewarded, and b) Alice knows that K can never be divulged again.
-(Note: in order to know that the secure channel private key was truly destroyed, we have to protect against replay attacks using a secure counter as in Flicker section 4.3.2.)
-
-\item If Charlie doesn't claim his key-destruction payment before time T, Alice knows that something is wrong.
-We can strengthen this to "Charlie loses reputation" by having him sign a promise to destroy the key at the start.
-
-Note that the protocol as written does not restrict to whom Charlie divulges the key. However, it produces a non-repudiable record of the persons to whom it has been divulged.
-
-\end{enumerate}
+The protocol as written does not restrict to whom Charlie divulges $K$; it simply produces a non-repudiable record of the divulgences.
+Suppose that Alice wishes that only Bob (or some arbitrary set of identities) is able to receive $K$.
+She could write the Ethereum contract in such a way that only a log that contains two entries---one corresponding to Bob and another indicating key destruction---can be used to claim the commission.
+If Alice wishes to make it impossible to divulge $K$ to someone other than Bob, she can embed Bob's key into the PAL.
+The TPM will guarantee that any modification to the PAL will produce an invalid attestation.
 

### 2016-05-18 paper.tex
Vanish description.

@@
 
-Vanish\\
+One solution to the expiring message problem was proposed in 2009 by Geambasu, Kohno, Levy, and Levy as ``Vanish: Increasing Data Privacy with Self-Destructing Data.'' The Vanish protocol runs as follows:
+
+\begin{itemize}
+\item Alice encrypts her data using random key $K$
+\item Alice divides $K$ into $N$ threshold secret shares (following Shamir 1979) and destroys the original copy 
+\item Alice stores all $N$ shares in a distributed hash table (DHT) at pseudo-random indices
+\item Alice sends to Bob the ciphertext of the data as well as the seed used to derive the share indices
+\item Bob uses the indices to retrieve $M$ shares of the key, which he uses to decrypt the ciphertext
+\end{itemize}
+
+In order to achieve the expiring property, Vanish relies on the behavior of the DHT.
+The prototype uses the Vuze DHT, which expunges stored data after 8 hours, and requires republishing to persist the data beyond that interval.
+Other DHT implementations like OpenDHT allow the user to specify an expiration interval.
+
+Subsequent work by Wolchok et al.
+(``Defeating Vanish with Low-Cost Sybil Attacks Against Large DHTs'') demonstrated how to defeat Vanish by crawling the Vuze DHT for all stored values.
+In a follow-up paper (``New Directions for Self-Destructing Data Systems"), the Vanish authors proposed methods for hardening the Vuze DHT against crawling, as well as mechanisms for splitting the key between different types of stores.
+
+The fundamental assumption behind Vanish is that we can trust most nodes to behave correctly, and that securing the system is therefore a matter of raising the threshold number of nodes that must abuse that trust before the system fails.
+Our work differs in that we do not assume that the third-party key store behaves correctly.
+If the key store behaves correctly, it can provably attest to doing so.
+If it fails to produce this attestation, Alice can infer that the key store misbehaved.
 

### 2016-05-18 paper.tex
added bib

@@
 
-One solution to the expiring message problem was proposed in 2009 by Geambasu, Kohno, Levy, and Levy as ``Vanish: Increasing Data Privacy with Self-Destructing Data.'' The Vanish protocol runs as follows:
+One solution to the expiring message problem was proposed in 2009 by Geambasu, Kohno, Levy, and Levy as ``Vanish: Increasing Data Privacy with Self-Destructing Data''~\cite{vanish}.
+The Vanish protocol runs as follows:
 
@@
 Other DHT implementations like OpenDHT allow the user to specify an expiration interval.
-
 Subsequent work by Wolchok et al.
-(``Defeating Vanish with Low-Cost Sybil Attacks Against Large DHTs'') demonstrated how to defeat Vanish by crawling the Vuze DHT for all stored values.
+(``Defeating Vanish with Low-Cost Sybil Attacks Against Large DHTs''~\cite{defeat-vanish}) demonstrated how to defeat Vanish by crawling the Vuze DHT for all stored values.
 In a follow-up paper (``New Directions for Self-Destructing Data Systems"), the Vanish authors proposed methods for hardening the Vuze DHT against crawling, as well as mechanisms for splitting the key between different types of stores.
-
 The fundamental assumption behind Vanish is that we can trust most nodes to behave correctly, and that securing the system is therefore a matter of raising the threshold number of nodes that must abuse that trust before the system fails.
@@
 
-Flicker\\
+Flicker~\cite{flicker,iso-tpm}\\
 
-Ethereum\\
+Ethereum~\cite{ethereum-white,ethereum-yellow}\\
 
@@
 
+\bibliographystyle{unsrt}
+\bibliography{paper}
+
 \end{document}

### 2016-05-18 paper.tex
a rough draft of intro, related work, and conclusion, and some restructuring throughout

@@
 
-\usepackage[letterpaper, margin=1.0in]{geometry}
+\usepackage[letterpaper, margin=1.25in]{geometry}
 
@@
 
-Why it would be desirable to have information expire...
+Today, we have more choices than ever when it comes to deciding who can hold on to our sensitive data, but it can be difficult to know who to trust.
+Even though we may trust a party at a given time, it can be difficult to know who we can trust in the future and impossible to know who might be compromised or subpeonaed.
+In recent years, there have been an increasing number of cases where courts mandated that a given thid party hand over its encryption keys~\cite{hushmail}, and there has been increasing pressure from law enforcement for services to incorporate a government ``back-door''~\cite{backdoor}.
 
-The difficult problem in implementing information that expires is the impossibility of proving a negative.
-Even if it were possible for the recipient to prove that he has deleted the sensitive information, he can not prove that he didn't make a copy of it beforehand.
+These situations could be mitigated by the existence of a system in which sensitive data expired after a given time. In this paper, we attempt to provide one possible realization of such a system.
+%In this paper, we attempt to provide a solution to these problems with a system that automatically expires data after a given time period without requiring the explicit action of the end-user.
 
-This changes with the use of TPMs.
-With TPMs, it is possible to seal information such that it can only be accessed by a trusted program.
-Moreover, one can provably attest that the trusted program was executed with a given input and produced a given output.
+The difficulty in implementing expiring information lies in the difficulty of proving a negative.
+Namely, whoever is holding on to the sensitive data must prove not only that they deleted the data, but also that they didn't make a copy of it beforehand.
 
-Background on TPMs...
+In order to achieve this property, we leverage two areas of prior work on cryptographic proofs-of-work: Trusted Platform Modules (TPMs), and Ethereum smart contracts.
+TPMs allow one to ensure that code has been executed correctly and without modification, and smart contracts allow for the creation of an incentive system that encourages and rewards good behavior.
 
-sealed storage
-Secure channel
-Protection against replay attacks
+The rest of the paper is organized as follows.
+In Section 2, we provide background information on TPMs and Ethereum, and discuss prior work on expiring information.
+In Section 3, we make explicit our attack model and the goals of our protocol.
+In Section 4, we present our protocol and in Section 5, we analyze both the security properties it achieves and the limitations in entails.
+We conclude in Section 6.
 
-\section{Related Work}
+\section{Background and Related Work}
 
-One solution to the expiring message problem was proposed in 2009 by Geambasu, Kohno, Levy, and Levy as ``Vanish: Increasing Data Privacy with Self-Destructing Data''~\cite{vanish}.
-The Vanish protocol runs as follows:
+\subsection{Expiring Data}
+
+One solution to the expiring message problem was the ``Vanish'' system, proposed by Geambasu et al. in 2009~\cite{vanish}. The Vanish protocol runs as follows:
 
@@
 The prototype uses the Vuze DHT, which expunges stored data after 8 hours, and requires republishing to persist the data beyond that interval.
-Other DHT implementations like OpenDHT allow the user to specify an expiration interval.
-Subsequent work by Wolchok et al.
-(``Defeating Vanish with Low-Cost Sybil Attacks Against Large DHTs''~\cite{defeat-vanish}) demonstrated how to defeat Vanish by crawling the Vuze DHT for all stored values.
-In a follow-up paper (``New Directions for Self-Destructing Data Systems"), the Vanish authors proposed methods for hardening the Vuze DHT against crawling, as well as mechanisms for splitting the key between different types of stores.
+Other DHT implementations, such as OpenDHT, allow the user to specify an expiration interval~\cite{vanish}.
+
+However, subsequent work by Wolchok et al. demonstrated that Vanish can be defeated (relatively cheaply) by crawling the Vuze DHT for all stored values~\cite{defeat-vanish}.
+
 The fundamental assumption behind Vanish is that we can trust most nodes to behave correctly, and that securing the system is therefore a matter of raising the threshold number of nodes that must abuse that trust before the system fails.
@@
 
-Flicker~\cite{flicker,iso-tpm}\\
+\subsection{Trusted Platform Modules}
 
-Ethereum~\cite{ethereum-white,ethereum-yellow}\\
+A Trusted Platform Module (TPM) is a dedicated, tamper-resistant hardware module that can provide a provable attestation of the current platform state to an external entity.
+The platform state is made up of a log of hashes of software events and a set of registers whose value is a function of the entire log of events.
+In response to a challenge nonce, the TPM provides (1) this untrusted log of events, and (2) a \textit{quote}, which is a digital signature covering the nonce and the current register values.
+An external entity can verify the log by using it to recompute the register values and confirming that they match those in the quote.
+Furthermore, the external entity can verify the legitamcy of the signature by validating the certificate chain of the TPM's public key and deciding whether or not to trust the issuing certificate authority~\cite{tpm-iso}.
 
-\section{Design}
+Flicker is an infrastructure built on top of TPMs that reduces the set of code that must be trusted and verified to only Flicker (250 lines of code) and the Piece of Application Logic (PAL) itself, as opposed to the entire operating system.
+This provides more meaningful attestations that users can reason about and thus provides a more practical trust model for our purposes.
+
+Flicker introduces two important features that will provide the basis of our system protocol.
+First, it provides replay-resistant sealed storage.
+This mechanism takes as input a piece of sensitive data and a set of register values, $R$, which represents the state that must be held by the PAL in order to retreieve the values.
+In order to unseal the data, a PAL (either a later invocation of the original code or an entirely different PAL) must call the unseal command while executing with exactly the software state $R$.
+For example, if a rootkit were to be added after sealing the original data, the PAL would no longer be able to access the sealed data until the rootkit were removed because its presence would unpredictably alter the register values.
+
+Second, Flicker introduces the notion of a TPM-based secure communication channel, which can be established as follows: (1) the PAL generates an asymmetric keypair within the protections of Flicker and puts this into sealed storage as described above, (2) the PAL transmits the public key along with an attestation to some remote party, (3) the remote party uses the attestation to verify that the PAL produced the provided public key.
+Once this one-way channel from the PAL to the remote party has been established, the remote party can use the PAL's public key to initiate a secure channel in the other direction~\cite{flicker}.
+
+\subsection{Ethereum}
+
+Ethereum is a generalized, programmable blockchain platform inspired by Bitcoin that allows anyone to easily create and run arbitrary decentralized applications.
+Ethereum is based upon two building blocks: ``accounts,'' which consist of a nonce, a balance, a piece of code, and storage, and ``Ether,'' which is an Ethereum-specific cryptocurrency used to pay transaction fees.
+
+There are two types of accounts, both of which can maintain an ether balance and send  transactions: externally-controlled accounts, and contracts.
+Only externally-controlled accounts can initiate transactions, but contracts can fire transactons in response to others they have received.
+A transaction could be a simple transfer of ether, or could involve running a piece of the contract's code that updates its state.
+
+Contracts are written in a high-level language and compiled down to an Ethereum-specific binary, which is then uploaded onto the blockchain.
+Once uploaded, the contract will exist and operate as long as the Ethereum network exists unless it is programmed to stop~\cite{ethereum-white}.
+
+\section{Problem}
+
+\subsection{Attack Model}
 
@@
 
-As a straw man, Alice could send the message to Bob encrypted with key $K$, and then store $K$ on a trusted third party (Charlie).
-To read the data, Bob asks Charlie for $K$, and if the current time is less than $t$, Charlie gives it to him.
+\subsection{Design Goals}
+
+\section{Protocol}
+
+\subsection{Strawman}
+
+As a strawman, Alice could send the message to Bob encrypted with key $K$, and then store $K$ on a trusted third party (Charlie).
+To read the data, Bob asks Charlie for $K$, and if the current time is less than $t$, Charlie returns it.
 Just as we assume that Bob will not make a copy of the message, we assume that he discards $K$ after each use.
@@
 
-Through use of a TPM, we can shift the burden of proof onto Charlie; instead of Alice proving that Charlie acted in bad faith, Charlie can prove that he acted correctly.
-Suppose, for example, that we extend the model such that Charlie is a provider of secure computing.
-In exchange for a fee, he will provide attestable execution of a given program at a given time.
+\subsection{PAL}
 
-Alice and Charlie can perform a protocol as follows:
+The key insight of our approach is that, through the use of a TPM, we can shift the burden of proof onto Charlie; instead of Alice proving that Charlie acted in bad faith, Charlie can prove that he acted correctly.
+Specifically, we mandate that Charlie is a provider of secure computing, who, in exchange for a fee, will provide attestable execution of a given program at a given time.
+
+At the center of this approach is a Flicker PAL, which can be run in one of three modes:
+
+\begin{itemize}
+\item \texttt{initialize()} -- This function generates a public/private key pair
+\item \texttt{divulge(log)} -- ...
+\item \texttt{destroy(log)} -- ...
+\end{itemize}
+
+\subsection{Contracts}
+
+\begin{itemize}
+\item Explicit, high? cost to join
+\item Force to put deposit in for each transsaction, only get it back when the Ethereum contract ends
+\end{itemize}
+
+\subsection{Protocol}
+
+With the previous building blocks in place, we now enumerate our protocol for attestable expiration of sensitive data:
 
@@
 
-\item Alice sends a Flicker PAL to Charlie. The PAL has an input parameter called `mode' which can take one of the following values: `initialize', `divulge', or `destroy'.
+\item Alice sends a Flicker PAL to Charlie. The PAL has an input parameter, ``mode,'' which can take one of three: \texttt{initialize}, \texttt{divulge}, or \texttt{destroy}.
 
-\item Alice asks Charlie to run the PAL with the input `mode=initialize'.
+\item Alice asks Charlie to run the PAL with the mode \texttt{initialize}.
 When Charlie runs the PAL, the PAL establishes a secure channel.
@@
 
-\item When the PAL is run using `mode=divulge', it also produces as output an append-only log that contains one entry for every public key to whom Charlie has divulged $K$.
+\item When the PAL is run using mode \texttt{divulge}, it also produces as output an append-only log that contains one entry for every public key to whom Charlie has divulged $K$.
 The log is signed using the secure channel private key.
 This log must be included on subsequent executions that use `mode=divulge' so that the PAL can add another entry if necessary.
-The PAL can confirm that the required log has been provided and protect against replay attacks by using a monotonic counter, described in Flicker 4.3.2.
+The PAL can confirm that the required log has been provided and protect against replay attacks by using a monotonic counter, described in Flicker 4.3.2~\ref{flicker}.
 
@@
 
+\section{Conclusion}
+
+In this paper, we presented a solution for attestable expiration of sensitive data based on TPMs and Ethereum smart contracts.
+TPMs allow a third-party to provide a cryptographic attestation of who they shared the data with and at what time they deleted the data, while smart contracts both provide incentives for good behavior and explicitly punish bad behavior in our system.
+Furthermore, the popularity of the Ethereum platform (and blockchain-based protocols in general) and the fact that TPMs are now shipping on almost all modern processors make this system both feasible and practical with current techbnologies.
+
 \bibliographystyle{unsrt}

### 2016-05-18 paper.tex
Minor edits.

@@
 
-Today, we have more choices than ever when it comes to deciding who can hold on to our sensitive data, but it can be difficult to know who to trust.
+Today, we have more choices than ever when it comes to deciding who can hold on to our sensitive data, but it can be difficult to know whom to trust.
 Even though we may trust a party at a given time, it can be difficult to know who we can trust in the future and impossible to know who might be compromised or subpeonaed.
-In recent years, there have been an increasing number of cases where courts mandated that a given thid party hand over its encryption keys~\cite{hushmail}, and there has been increasing pressure from law enforcement for services to incorporate a government ``back-door''~\cite{backdoor}.
+In recent years, there have been an increasing number of cases where courts mandated that a given third party hand over its encryption keys~\cite{hushmail}, and there has been increasing pressure from law enforcement for services to incorporate a government ``back-door''~\cite{backdoor}.
 
@@
 
-In order to achieve this property, we leverage two areas of prior work on cryptographic proofs-of-work: Trusted Platform Modules (TPMs), and Ethereum smart contracts.
-TPMs allow one to ensure that code has been executed correctly and without modification, and smart contracts allow for the creation of an incentive system that encourages and rewards good behavior.
+In order to achieve this property, we leverage two areas of prior work: Trusted Platform Modules (TPMs), and Ethereum smart contracts.
+TPMs allow one to provable attest that a given piece of code has been executed without modification, along with its inputs and outputs, and smart contracts allow for the creation of an incentive system that encourages and rewards good behavior.
 

### 2016-05-18 paper.tex
updates to 1,2,and 3

--- 2016-05-18 paper.tex
@@
 \usepackage[letterpaper, margin=1.25in]{geometry}
+\setlength{\parskip}{\baselineskip}%
+\setlength{\parindent}{0pt}%
 
@@
 
-Today, we have more choices than ever when it comes to deciding who can hold on to our sensitive data, but it can be difficult to know who to trust.
-Even though we may trust a party at a given time, it can be difficult to know who we can trust in the future and impossible to know who might be compromised or subpeonaed.
-In recent years, there have been an increasing number of cases where courts mandated that a given thid party hand over its encryption keys~\cite{hushmail}, and there has been increasing pressure from law enforcement for services to incorporate a government ``back-door''~\cite{backdoor}.
+Today, we have more choices than ever when it comes to deciding who can hold on to our sensitive data, and it is difficult to know who we can trust.
+Even though we may trust a party at a given time, it is impossible to know who might be compromised or subpeonaed in the future.
+In recent years, there have been an increasing number of cases where courts mandated that a third party hand over its encryption keys~\cite{hushmail}, and there has been increasing pressure from law enforcement for services to incorporate a government ``back-door''~\cite{backdoor}.
+Also, data is copied so cheaply and freely that even if we explicitly delete some piece of data through an application's API, there is no mechanism in place to ensure us that \textit{all} copies have been deleted, or that it has not been shared with some other party.
 
-These situations could be mitigated by the existence of a system in which sensitive data expired after a given time. In this paper, we attempt to provide one possible realization of such a system.
-%In this paper, we attempt to provide a solution to these problems with a system that automatically expires data after a given time period without requiring the explicit action of the end-user.
-
+These situations could be mitigated by the existence of a system in which sensitive data expired after a given time.
+In this paper, we attempt to provide one possible realization of such a system.
 The difficulty in implementing expiring information lies in the difficulty of proving a negative.
 Namely, whoever is holding on to the sensitive data must prove not only that they deleted the data, but also that they didn't make a copy of it beforehand.
-
 In order to achieve this property, we leverage two areas of prior work on cryptographic proofs-of-work: Trusted Platform Modules (TPMs), and Ethereum smart contracts.
@@
 The rest of the paper is organized as follows.
-In Section 2, we provide background information on TPMs and Ethereum, and discuss prior work on expiring information.
+In Section 2, we provide necessary background information on TPMs and Ethereum, and discuss prior work on expiring information.
 In Section 3, we make explicit our attack model and the goals of our protocol.
@@
 Other DHT implementations, such as OpenDHT, allow the user to specify an expiration interval~\cite{vanish}.
-
-However, subsequent work by Wolchok et al. demonstrated that Vanish can be defeated (relatively cheaply) by crawling the Vuze DHT for all stored values~\cite{defeat-vanish}.
+However, subsequent work by Wolchok et al.
+demonstrated that Vanish can be defeated (relatively cheaply) by crawling the Vuze DHT for all stored values~\cite{defeat-vanish}.
 
@@
 
+Suppose that Alice wishes to make a piece of sensitive data ($D$) available to Bob that expires at time $t$, without requiring that she be online after sending the data.
+That is, before time $t$ Bob is able to read the data whenever he pleases, but after time $t$ he is unable to read the data.
+In addition, no one other than Bob (defined more precisely as any entity having access to Bob's private key) should be able to decrypt the data at \textit{any} time.
+We denote the receipient of sensitive data, Bob, as a single party for simplicity, but we also desire the property that Bob could be replaced with a set of users without sacrificing any of the other properties.
+
 \subsection{Attack Model}
 
-Suppose that Alice wishes to send a message to Bob that expires at time $t$.
-That is, before time $t$ Bob is able to read the message, but after time $t$ Bob is unable to read the message.
-In our model, Bob is not malicious and will not attempt to make an illicit copy of the message.
-However, we wish to protect against the eventuality that Bob becomes malicious in the future, or that Bob's system is compromised by a future adversary (Mallory).
-We do not wish to require that Alice be online in order for Bob to receive or read the message.
-
-\subsection{Design Goals}
+In this model, we make the assumption Bob is not malicious and will not attempt to store an illicit (unencrypted) copy of the message, or share his private key with other individuals.
+However, we wish to protect against the eventuality that Bob becomes malicious in the future (after $t$), or that Bob's system is compromised by a future adversary (Mallory), either legally or illegally.
+We assume in this case that at any time after $t$ Mallory can gain full access to Bob's machine, including any encryption keys stored on it.
 
@@
 
-The problem with the straw man is that it requires extending the same trust to Charlie that we do to Bob.
+The problem with this approach is that it requires extending the same trust to Charlie that we do to Bob.
 Charlie can retain $K$ as long as he likes and distribute it as widely as he wishes---e.g., to Mallory---and moreover he can repudiate his misbehavior without any way for Alice to prove otherwise.
@@
 
-At the center of this approach is a Flicker PAL, which can be run in one of three modes:
+At the center of this approach is our custom Flicker PAL, which can be run in one of three modes:
 

### 2016-05-18 paper.tex
merged phils changes back in

@@
 
-Today, we have more choices than ever when it comes to deciding who can hold on to our sensitive data, and it is difficult to know who we can trust.
+Today, we have more choices than ever when it comes to deciding who can hold on to our sensitive data, and it is difficult to know whom to trust.
 Even though we may trust a party at a given time, it is impossible to know who might be compromised or subpeonaed in the future.
 In recent years, there have been an increasing number of cases where courts mandated that a third party hand over its encryption keys~\cite{hushmail}, and there has been increasing pressure from law enforcement for services to incorporate a government ``back-door''~\cite{backdoor}.
-Also, data is copied so cheaply and freely that even if we explicitly delete some piece of data through an application's API, there is no mechanism in place to ensure us that \textit{all} copies have been deleted, or that it has not been shared with some other party.
+Also, data is copied so cheaply and freely that even if we explicitly delete some piece of data through an application's API, there is no mechanism in place to ensure us that \textit{all} copies have been deleted, or that none of them have not been shared with some other party.
 
@@
 Namely, whoever is holding on to the sensitive data must prove not only that they deleted the data, but also that they didn't make a copy of it beforehand.
-In order to achieve this property, we leverage two areas of prior work on cryptographic proofs-of-work: Trusted Platform Modules (TPMs), and Ethereum smart contracts.
-TPMs allow one to ensure that code has been executed correctly and without modification, and smart contracts allow for the creation of an incentive system that encourages and rewards good behavior.
+In order to achieve this property, we leverage two areas of prior work: Trusted Platform Modules (TPMs), and Ethereum smart contracts.
+TPMs allow one to provably attest that a given piece of code has been executed without modification, along with its inputs and outputs, and smart contracts allow for the creation of an incentive system that encourages and rewards good behavior.
 

### 2016-05-18 paper.tex
Intro edits.

@@
 
-Today, we have more choices than ever when it comes to deciding who can hold on to our sensitive data, and it is difficult to know whom to trust.
-Even though we may trust a party at a given time, it is impossible to know who might be compromised or subpeonaed in the future.
+As data storage becomes cheaper and cheaper, the cost of archiving communication approaches zero.
+As a society, however, we have an interest in being able to leave the past behind.
+We recognize the value of the ephemeral, especially since private communications may become public through malice or legal action.
+
+Encryption can be used to make communications private, but that only begs the question of access to the key.
 In recent years, there have been an increasing number of cases where courts mandated that a third party hand over its encryption keys~\cite{hushmail}, and there has been increasing pressure from law enforcement for services to incorporate a government ``back-door''~\cite{backdoor}.
-Also, data is copied so cheaply and freely that even if we explicitly delete some piece of data through an application's API, there is no mechanism in place to ensure us that \textit{all} copies have been deleted, or that none of them have not been shared with some other party.
 
-These situations could be mitigated by the existence of a system in which sensitive data expired after a given time.
+What we might desire is to be able to enforce the ephemerality of some data, such that all copies of that data are not readable after a user-defined point in time.
 In this paper, we attempt to provide one possible realization of such a system.
-The difficulty in implementing expiring information lies in the difficulty of proving a negative.
-Namely, whoever is holding on to the sensitive data must prove not only that they deleted the data, but also that they didn't make a copy of it beforehand.
-In order to achieve this property, we leverage two areas of prior work: Trusted Platform Modules (TPMs), and Ethereum smart contracts.
+
+The difficulty in implementing expiring information lies in the impossibility of proving a negative.
+Even if it were possible for the holder of sensitive data to prove that he has deleted it, he can not prove that he didn't make a copy of it beforehand.
+However, recent developments in computer hardware have enabled us to prove a rough equivalent, namely that data has only been accessed under certain conditions.
+
+We leverage two areas of prior work: Trusted Platform Modules (TPMs), and Ethereum smart contracts.
 TPMs allow one to provably attest that a given piece of code has been executed without modification, along with its inputs and outputs, and smart contracts allow for the creation of an incentive system that encourages and rewards good behavior.

### 2016-05-18 paper.tex
almost done section 4 rewrite

@@
 That is, before time $t$ Bob is able to read the data whenever he pleases, but after time $t$ he is unable to read the data.
-In addition, no one other than Bob (defined more precisely as any entity having access to Bob's private key) should be able to decrypt the data at \textit{any} time.
+%In addition, no one other than Bob (defined more precisely as any entity having access to Bob's private key) should be able to decrypt the data at \textit{any} time.
 We denote the receipient of sensitive data, Bob, as a single party for simplicity, but we also desire the property that Bob could be replaced with a set of users without sacrificing any of the other properties.
@@
 
-\subsection{PAL}
+\subsection{Design}
 
@@
 \begin{itemize}
-\item \texttt{initialize()} -- This function generates a public/private key pair
-\item \texttt{divulge(log)} -- ...
-\item \texttt{destroy(log)} -- ...
-\end{itemize}
-
-\subsection{Contracts}
-
-\begin{itemize}
-\item Explicit, high? cost to join
-\item Force to put deposit in for each transsaction, only get it back when the Ethereum contract ends
+\item \texttt{initialize()} -- This function generates the first half of a TPM-based secure communication channel as described in Section~\ref{sec:tpm}.
+Namely, it generates a public/private key pair, stores the private key using the TPM's sealed storage mechanism, and outputs the public key.
+\item \texttt{divulge($C$,$PK$,log)} -- The function takes as input an append-only log of every
+\item \texttt{destroy(log)} --
 \end{itemize}
@@
 
-With the previous building blocks in place, we now enumerate our protocol for attestable expiration of sensitive data:
+With the previous building blocks in place, we now enumerate our protocol for attestable expiration of sensitive data.
+For now, we make the assumption that Alice has decided on a few things out-of-band:
+
+\begin{itemize}
+\item A specific third-party, Charlie, based on her preferences for reliability vs. cost
+\item The cost of storing the data, which Alice will pay to Charlie if he behaves honestly, $C_{store}$
+\item The collateral that Charlie must put up in order to participate in the system, $C_{collateral}$, which makes explicit the cost of Charlie acting maliciously
+\end{itemize}
+
+We leave details of the reputation system, including the algorithm for generating these parameters based on the third-party's reputation, and the process of matching users with third-parties to future work.
 
@@
 
-\item Alice sends a Flicker PAL to Charlie. The PAL has an input parameter, ``mode,'' which can take one of three: \texttt{initialize}, \texttt{divulge}, or \texttt{destroy}.
+\item Charlie creates an Ethereum smart contract, which takes as input Charlie's $C_{collateral}$ and Alice's $C_{store}$ and promises the following:
+\begin{itemize}
+\item If Charlie produces an attestation that proves he deleted Alice's data before $t$, the contract returns to Charlie his initial collateral and the price paid by Alice.
+This contract remains on the blockchain as a piece of evidence of Charlie's honesty for future parties to reference as part of the reputation system.
+\item If Charlie does not produce an attestation before $t$, the contract returns $C_{store}$ to Alice and Charlie receives nothing.
+Consequently, this contract remains on the blockchain as a piece of evidence of Charlie's \textit{dishonesty}.
+\end{itemize}
 
-\item Alice asks Charlie to run the PAL with the mode \texttt{initialize}.
-When Charlie runs the PAL, the PAL establishes a secure channel.
-That is, it generates a public/private key pair, outputs the public key, and stores the private key in the TPM such that only this PAL is able to read it.
+\item Alice sends the custom Flicker PAL to Charlie, and a nonce, $n$.
 
-\item Charlie sends Alice the PAL's output as well as a Flicker attestation of the execution.
-After verifying the attestation, Alice knows that a) her PAL was executed, and b) it produced the attested public key.
+\item Charlie runs \texttt{PAL.initialize()}, which outputs the secure channel public key, $PK_{PAL}$, and then creates an attestation, $Attest_{initialize}$, that he ran the function correctly, based on $n$.
 
-\item Alice encrypts $K$ with the secure channel public key and sends it to Charlie.
-Charlie stores the ciphertext of $K$.
-Alice then goes offline, but not before writing an Ethereum contract, described below as step 8.
+\item Charlie sends $PK_{PAL}$ and $Attest_{initialize}$ to Alice. After verifying the attestation, Alice knows that (a) her PAL was executed, and (b) it produced $PK_{PAL}$.
 
-\item In order to request $K$, Bob sends his public key to Charlie.
-Charlie runs the PAL with three inputs: `mode=divulge', the ciphertext of $K$, and Bob's public key.
-The PAL decrypts $K$ using the secure channel private key, re-encrypts it using Bob's public key, and produces the re-encrypted key as output.
-Charlie sends the output to Bob.
+\item Alice encrypts her sensitive data $D$ using $PK_{PAL}$, to produce $C_{D,PK_{PAL}}$, which she sends to Charlie, and then goes offline.
 
-\item When the PAL is run using mode \texttt{divulge}, it also produces as output an append-only log that contains one entry for every public key to whom Charlie has divulged $K$.
-The log is signed using the secure channel private key.
-This log must be included on subsequent executions that use `mode=divulge' so that the PAL can add another entry if necessary.
-The PAL can confirm that the required log has been provided and protect against replay attacks by using a monotonic counter, described in Flicker 4.3.2~\ref{flicker}.
+\item In order to request $D$, Bob sends his public key, $PK_{Bob}$, to Charlie
 
-\item If Charlie runs the PAL with inputs comprising `mode=destroy' and the divulgence log, the PAL will append to the log the statement ``key destroyed''.
-It will then destroy the secure channel private key.
+\item Charlie runs \texttt{PAL.divulge($C_{D,PK_{PAL}}$,$PK_{Bob}$,log)}, which decrypts the original data and outputs (1) the data re-encrypted with $PK_{Bob}$,  $C_{D,PK_{Bob}}$ and a copy of the log with $PK_{Bob}$ appended, indicating that Charlie divulged $D$ to Bob.
 
-\item Before going offline, Alice wrote an Ethereum contract that said, ``If Charlie publishes before time $t$ a log that can be decrypted using this public key and whose last entry is ``key destroyed", I will pay him $X$ ether."
+\item Some time before $t$, Charlie runs \texttt{PAL.destroy(log)}, which deletes the encrypted data and outputs a copy of the log with ``data destroyed'' appended, and creates an attestation, $Attest_{destroy}$,
+
+\item Charlie then submits $Attest_{desotry}$ to the Ethereum contract in order to receive his payment.
 
@@
 
-If Charlie produces proof that he destroyed the key, he earns his commission and Alice knows that $K$ can never be divulged again.
-If he does not claim his commission before time $t$, then Alice knows that something is wrong.
-We can tie the protocol into a reputation system by requiring as step 0 that Charlie make a public, signed commitment to fulfilling the contract.
+If Charlie produces proof that he destroyed the key, he earns his commission and Alice knows that $D$ can never be divulged again.
+If he does not claim his commission before time $t$, then the Ethereum contract provides proof of Charlie's misbehavior, which would utlimately reflect his reputation and thus his ability to secure future contracts.
 
-The protocol as written does not restrict to whom Charlie divulges $K$; it simply produces a non-repudiable record of the divulgences.
-Suppose that Alice wishes that only Bob (or some arbitrary set of identities) is able to receive $K$.
+The protocol as written does not restrict to whom Charlie divulges $D$; it simply produces a non-repudiable record of the divulgences.
+Suppose that Alice wishes that only Bob (or some arbitrary set of identities) is able to receive $D$.
 She could write the Ethereum contract in such a way that only a log that contains two entries---one corresponding to Bob and another indicating key destruction---can be used to claim the commission.
-If Alice wishes to make it impossible to divulge $K$ to someone other than Bob, she can embed Bob's key into the PAL.
+If Alice wishes to make it impossible to divulge $D$ to someone other than Bob, she can embed Bob's key into the PAL.
 The TPM will guarantee that any modification to the PAL will produce an invalid attestation.
+
+In addition, the protocol does not explicitly handle the case where Charlie either (1) deletes the key at some time $t_d << t$ or (2) goes offline after receiving $D$ but comes back online and successfully produces $Attest_{delete}$ before $t$.
+These too could be incorporated into the Ethereum contract, in which Bob could report cases of $D$ being unavailable before $t$, which would again affect Charlie's reputation.
 
@@
 TPMs allow a third-party to provide a cryptographic attestation of who they shared the data with and at what time they deleted the data, while smart contracts both provide incentives for good behavior and explicitly punish bad behavior in our system.
-Furthermore, the popularity of the Ethereum platform (and blockchain-based protocols in general) and the fact that TPMs are now shipping on almost all modern processors make this system both feasible and practical with current techbnologies.
+Furthermore, the popularity of the Ethereum platform (and blockchain-based protocols in general) and the fact that TPMs are now shipping on almost all modern processors make this system both feasible and practical with current technologies.
 
